INTELLIGENT SYSTEMS

### 2021-04-18 papers/paper_9.tex
finish 9.4.4

>>>>

\subsection{NETWORK ARCHITECTURE AND TRAINING}
\subsubsection{IE-CNN Module}
The IE-CNN network takes care of having to extract the external and internal 
fetures and to do this there are two modules arranged on two different 
branches, one called EI-CNN branch and the other called trunk branch. The 
latter produces an output $T (x)$ where $x$ represents the input that is weighed 
down by a mask $F (x)$ of the same size. The result obtained represents 
the input of the algorithm $H (x)$. The IE-CNN branch has a number of 
convolutional layers $p$ equal to 3, while in the other branch the number of 
convolutional layers $q$ is equal to 2. For the construction of the trunk branch 
a pre-activation Residual Unit is used \cite{0902694026}, while in the other branch 
a customized large-size pre-activation Residual Unit is used. Other optimizations 
have been added for the model to achieve good performance.

\subsubsection{Pre-Activation Residual Unit}
IE-CNN training is carried out using the Stochastic Gradient Descent (SGD). 
Batch normalization and the ReLu activation function are used and both 
operate before the convolution operation with the aim of speeding up training 
and reducing the problem of covariates shift.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper9/architecture.png}
    \centering
    \caption{(a) Structure of pre-activation residual unit (b) the large-size one}
    \label{fig:ResidualUnit}
\end{figure}

\subsubsection{Architecture}
The IE-CNN branch structure is the one shown in figure \ref{fig:IE-CNN ARCHITECTURE}. The local pathway 
is used to extract internal features and to improve fine-grained recognition 
performance. The global pathway instead captures the external features. 
The integration of all these features is carried out with a max-out merger 
strategy.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper9/IE-CNN.png}
    \centering
    \caption{IE-CNN branch.}
    \label{fig:IE-CNN ARCHITECTURE}
\end{figure}

\subsubsection{Framework of the proposed training method}
The proposed model maps each image in a Euclidean space where, through 
the use of the distance L2, its similarity will be established. Following the 
\emph{LMNN} method \cite{0902694039}, three sets of images are created:
\begin{enumerate}
    \item $x^o$ (\emph{original}): represents the image of the face of a single individual;
    \item $x^p$ (\emph{positive}): represents the remaining images of the same individual;
    \item $x^n$ (\emph{positive}): represent the images of the faces of the other different 
    individuals.
\end{enumerate}
The aim is to have smaller Euclidean distances between $x^o$ and $x^p$. The 
input of the network consists of mini-batches, composed of images of positive 
and negative faces, composed of a few images useful for obtaining a better 
convergence during the descent of the stochastic gradient. In order to select 
the best set triples useful for training, the strategy to be used is to consider 
a $\theta$ margin in which the negative images $x^n$  will be found. Positive and 
negative image sets that have maximum distance will be chosen. 
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.4\linewidth]{images/paper9/SET.png}
    \centering
    \caption{High-dimensional space.}
    \label{fig:HDS}
\end{figure}

The following are the steps performed on each original image $x^o$:
\begin{enumerate}
    \item Pre-processing: performed by a pre-trained CNN;
    \item Features enchancement: both external and internal;
    \item Mapping: in high-dimensional space.
\end{enumerate}
